FinalManuscript_DISCS_UG

### 2019-03-03 parts/02_relatedliterature.tex
Applied most comments for chapter 2
Add citation for scikit-image
WIP cryptosystem RRL
working on cryptosystem RRL
Done with first pass of sections 2.1 to 2.3 of RRL
Note: linebreaking in URLs in section 2.3 have to be addressed

We will now provide an overview of the \textit{CryptoImg} project, which our study is primarily based on. Then, we define the specific image processing operations we are interested in implementing in this study. Then we will introduce concepts in cryptography and define the four homomorphic cryptosystems we will be testing in the study.

\input{parts/02_relatedliterature_01cryptoimg}
\input{parts/02_relatedliterature_02commonimageprocessingoperations}
%facial recognition - theory
\input{parts/02_relatedliterature_03facialrecognition}
\input{parts/02_relatedliterature_04homomorphiccryptosystems}
\input{parts/02_relatedliterature_05partiallyhomomorphic}
\input{parts/02_relatedliterature_06fullyhomomorphic}
%facial recognition - implementation
\input{parts/02_relatedliterature_07previousimplementations}

>>>>

We will now describe homomorphic cryptosystems in detail to provide a concrete description of their current capabilities and limitations. Then, we will describe our target applications in image processing and facial recognition.

\input{parts/02_relatedliterature_04homomorphiccryptosystems}
\input{parts/02_relatedliterature_05partiallyhomomorphic}
\input{parts/02_relatedliterature_06fullyhomomorphic}
\input{parts/02_relatedliterature_01cryptoimg}
\input{parts/02_relatedliterature_02commonimageprocessingoperations}
%facial recognition - theory
\input{parts/02_relatedliterature_03facialrecognition}
%facial recognition - implementation
\input{parts/02_relatedliterature_07previousimplementations}

### 2019-03-03 parts/02_relatedliterature_05partiallyhomomorphic.tex
Done with first pass of sections 2.1 to 2.3 of RRL
Note: linebreaking in URLs in section 2.3 have to be addressed

In this section, we will present two classical partially homomorphic cryptosystems (PHEs) which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic and allow for the multiplication of a plaintext scalar. We will then show how these PHEs may be adapted for secure floating-point computation.

@@

\subsection{Floating-Point Arithmetic using PHEs}
\label{sec:fp_arithmetic}
We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers. We will now show how these PHEs may be extended to a system which allows for secure floating-point computation.

In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in a PHE, respectively.

>>>>

In this section, we will present two classical partially homomorphic encryption (PHE) schemes which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic and allow for the multiplication of a plaintext scalar. We will then show how these PHE schemes may be adapted for secure floating-point computation.

@@

\subsection{Floating-Point Arithmetic using PHE}
\label{sec:fp_arithmetic}
We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers. We will now show how these PHE schemes may be extended to a system which allows for secure floating-point computation.

In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in a PHE scheme, respectively.

### 2019-03-03 parts/02_relatedliterature_06fullyhomomorphic.tex
Done with first pass of sections 2.1 to 2.3 of RRL
Note: linebreaking in URLs in section 2.3 have to be addressed

We will also be testing fully homomorphic cryptosytems (FHEs), which allow aribitrary computation on encrypted data.

The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices. Gentry's original construction showed that fully homomorphic cryptosystems are possible, although they are known to be significantly slower than partially homomorphic cryptosytems. 
Improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.

We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research. Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe pertinent developements and implementations of each cryptosystem.

\subsection{DGHV Cryptosystem}
In 2009, Dijk, Gentry, Halevi, and Vaikuntanathan created a fully homomorphic cryptosystem which operates primarily through elementary modular arithmetic, commonly called the DGHV cryptosystem \cite{cryptoeprint:2009:616}. This was further improved in 2011 \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys, reducing the size of secure public keys from 12.5 GB to 2.5 MB.

The DGHV cryptosystem encrypts single bits as integer ciphertexts. XOR and AND binary operations on encrypted bits are achieved by modular addition and modular multiplication on the integer ciphertexts. When operations are performed on ciphertexts, noise accumulates in the ciphertexts, which may prevent successful decryption.

A C++ implementation of the improved DGHV cryptosystem \cite{cryptoeprint:2011:440} using the GNU Multiple Precision Arithmetic Library may be found at https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants.

For small security parameters, initial experiments using the DGHV cryptosystem have shown it takes 4.38 seconds for key generation, and

@@

For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency. Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.

>>>>

We will also be testing fully homomorphic encryption (FHEs), which allow aribitrary computation on encrypted data.

The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices. Gentry's original construction showed that FHE are possible, although they are known to be significantly slower than PHE. 
Improving the efficiency of FHis an active area of research \cite{sen_homomorphic_2013}.

We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research. Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe important developments and implementations of each cryptosystem.

\subsection{DGHV Cryptosystem}
In 2009, Dijk, Gentry, Halevi, and Vaikuntanathan created a fully homomorphic cryptosystem which operates primarily through elementary modular arithmetic, commonly called the DGHV cryptosystem \cite{cryptoeprint:2009:616}. This was further improved in 2011 by Coron, Naccache, and Tibouchi, \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys, reducing the size of secure public keys from 12.5 GB to 2.5 MB.

The DGHV cryptosystem encrypts single bits as integer ciphertexts. XOR and AND binary operations on encrypted bits are achieved by modular addition and modular multiplication on the integer ciphertexts. When operations are performed on ciphertexts, noise accumulates in the ciphertexts, which may prevent successful decryption. To eliminate this noise, a \textit{refresh} or \textit{recrypt} procedure is used to reduce noise in a ciphertext. The refresh procedure for DGHV involves operating on a ciphertext with a \textit{recryption matrix}, which is more time-intensive than key generation, encryption, decryption, addition, and multiplication procedures.

A Sage 4.7.2 implementation of the improved DGHV cryptosystem by Coron, et al. \cite{cryptoeprint:2011:440} may be found at \texttt{https://github.com/coron/fhe}. For small security parameters,  initial experiments using this implementation have shown it takes 0.06 seconds for key generation, 0.05 seconds for encryption, and 0.41 seconds for the recrypt procedure. For large security parameters, key generation takes 10 minutes, encryption takes 7 minutes and 15 seconds, and the recrypt procedure takes 11 minutes and 34 seconds \cite{cryptoeprint:2011:440}. Since the DGHV cryptosystem encrypts single plaintext bits, we can expect that operations on 32-bit floating point numbers are time-intensive, even under small security parameters.

A more recent C++ implementation of the improved DGHV cryptosystem \cite{cryptoeprint:2011:440} using the GNU Multiple Precision Arithmetic Library may be found at \texttt{https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants}. This implementation is more accessible than the original Sage 4.7.2 implementation, since the original code has compatibility issues with current versions of SageMath.

@@

One prominent implementation is \textit{HElib} (\texttt{https://github.com/shaih/HElib}) \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem C++ using the NTL mathematical library, with optimizations to improve efficiency. Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
